Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2014-01-20 paper/reply.tex
new reply

  However, there is a clear degeneracy between the minimum halo mass
  $M_{\rm min}$ and the occupation fraction.This trend is clearly
  seen on the right panel of Figure 3,4 and 6. This implies that
  exploring very low escape fractions values of the range $0.01$ would
  require building mock catalogs with a minimum mass around the range
  $10^{9.5}$Msun or below which is precisely the minimum halo mass of
  that is resolved in the simulation. This intrinsic limitation on the
  range of values that can be explored is now explicit in the paper.

>>>>

  However, there is a clear degeneracy between the minimum halo mass
  $M_{\rm min}$ and the occupation fraction.This trend is clearly
  seen on the right panel of Figure 3,4 and 6. This implies that
  exploring very low escape fractions values of the range $0.01$ would
  require building mock catalogs with a minimum mass below the range of
  $10^{9.5}$Msun which is precisely the minimum halo mass of
  that is resolved in the simulation. This intrinsic limitation on the
  range of values that can be explored is now explicit in the paper.
